Demographic Factors and Climate Action: Understanding How Age and Education Shape Sustainable Choices

### 2024-12-14 paper/climate_change.qmd
cant render because offig-nineteen

## Model Summary Table
@fig-nineteen presents the accuracy of models predicting climate-friendly actions based on age and education. A threshold emerges from the data: models with accuracy above 50% are considered reliable, while those below require careful interpretation. Sorting waste correctly, with an accuracy of 59%, is the most reliable prediction, indicating a stronger association between demographic factors and this behavior. Models like home improvements (33%) offer limited predictive value but remain somewhat informative. In contrast, actions such as adopting meat alternatives (25%) or choosing electric or hybrid vehicles (25%) approach random chance, making their predictions less reliable for drawing meaningful conclusions.

```{r}
#| warning: false
#| echo: false
#| message: false
#| results: hide
#| fig-cap: This table presents the accuracy of models predicting the likelihood of various climate-friendly actions based on age and education. See Table @fig-nineteen for details."
#| fig-names: model_accuracies

>>>>

## Model Summary Table
fig-nineteen presents the accuracy of models predicting climate-friendly actions based on age and education. A threshold emerges from the data: models with accuracy above 50% are considered reliable, while those below require careful interpretation. Sorting waste correctly, with an accuracy of 59%, is the most reliable prediction, indicating a stronger association between demographic factors and this behavior. Models like home improvements (33%) offer limited predictive value but remain somewhat informative. In contrast, actions such as adopting meat alternatives (25%) or choosing electric or hybrid vehicles (25%) approach random chance, making their predictions less reliable for drawing meaningful conclusions.

```{r}
#| warning: false
#| echo: false
#| message: false
#| results: hide
# #| label: fig-nineteen
#| fig-cap: This table presents the accuracy of models predicting the likelihood of various climate-friendly actions based on age and education.
